SunPy - Python for Solar Physics

### 2014-08-26 2-2-Lightcurve.tex
Solve #118 by removing reference to Factory.

Currently, the \texttt{LightCurve} class is compatible with the
following data sources: the \textit{GOES} X-ray Sensor (XRS), \textit{PROBA2}/LYRA, and \textit{SDO}/EVE\footnote{Note that only the level ``OCS'' and
average CSV files is currently implemented -- see \url{http://lasp.colorado.edu/home/eve/data/}}.  For each of these instruments, a subclass of the
\texttt{LightCurve} object is initialised
(e.g., \texttt{GOESLightCurve}) which inherits from
\texttt{LightCurve}, but allows instrument-specific functionality to be
included.  Future developments will introduce support for additional
instruments and data products, as well as implementing a factory interface 
similar to that of \texttt{Map}.  Since there is no established standard
as to how time-series data should be stored and distributed, each SunPy 
\texttt{LightCurve} object subclass provides the ability to download its corresponding 
specific data format in its constructor and parse that file type.

@@

\begin{listing}[H]
\pythoncode{lightcurve.py}
\begin{center}
\includegraphics[width=10cm]{goes_lightcurve.pdf}
\end{center}
\caption{Example retrieval of a GOES lightcurve
using a time range and the output of the 
\texttt{peek()} method. The maximum flux value in the \textit{GOES} 1.0--8.0$\AA$\ channel 
is then retrieved along with the location in time of the maximum.}
\label{code:goes_lc}
\end{listing}

>>>>

Currently, the \texttt{LightCurve} class is compatible with the
following data sources: the \textit{GOES} X-ray Sensor (XRS), \textit{PROBA2}/LYRA, and \textit{SDO}/EVE\footnote{Note that only the level ``OCS'' and
average CSV files is currently implemented -- see \url{http://lasp.colorado.edu/home/eve/data/}}.  For each of these instruments, a subclass of the
\texttt{LightCurve} object is initialised
(e.g., \texttt{GOESLightCurve}) which inherits from
\texttt{LightCurve}, but allows instrument-specific functionality to be
included.  Future developments will introduce support for additional
instruments and data products, as well as implementing an interface 
similar to that of \texttt{Map}.  Since there is no established standard
as to how time-series data should be stored and distributed, each SunPy 
\texttt{LightCurve} object subclass provides the ability to download its corresponding 
specific data format in its constructor and parse that file type.

@@

\begin{listing}[H]
\pythoncode{pycode_lightcurve.txt}
\begin{center}
\includegraphics[width=10cm]{goes_lightcurve.pdf}
\end{center}
\caption{Example retrieval of a GOES lightcurve
using a time range and the output of the 
\texttt{peek()} method. The maximum flux value in the \textit{GOES} 1.0--8.0$\AA$\ channel 
is then retrieved along with the location in time of the maximum.}
\label{code:goes_lc}
\end{listing}
